\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-07-31 sections/abstract.tex
Remove indent for keywords
Fixed typo

\begin{abstract}
  {
    \noindent
    Microorganisms naturally occur in communities which can consist of tens of thousands of species involved in complex interactions with each other.
    16S ribosomal RNA (rRNA) gene profiling provides snapshots that reveal the abundances and phylogenies of microorganisms in microbial communities.
    These snapshots can then be used to unveil the complex interactions governing these microbial communities.
    However, the nature of 16S data-sets makes the data processing difficult and error prone.
    The development of appropriate and well-validated analysis methods that do not produce statistical artifacts is still ongoing and is receiving much attention.
    Here, we perform a thorough analysis of each step in this process to determine the best tools and parameter choices that generate the most accurate and robust networks.
    Ultimately, we create a sequence analysis pipeline to standardize the processing of high-throughput community 16S rRNA sequencing data into networks of microbial interactions derived from their co-occurrences.
    \hl{The development of a standard pipeline for 16S data analysis would enable accurate comparison of data from different data-sets.} \todo[size=\footnotesize]{TODO: Talk briefly about the main result}
    The pipeline is availabe as a Python package and a docker container.
  }
\end{abstract}

% Insert keywords here
\setlength\parindent{.45in} \keywords{Microbiome, 16S rRNA, Pipeline, Interaction, Network, Correlations, Qiime}

>>>>

\begin{abstract}
  {
    \noindent
    Microorganisms naturally occur in communities which can consist of tens of thousands of species involved in complex interactions with each other.
    16S ribosomal RNA (rRNA) gene profiling provides snapshots that reveal the abundances and phylogenies of microorganisms in microbial communities.
    These snapshots can then be used to unveil the complex interactions governing these microbial communities.
    However, the nature of 16S data-sets makes the data processing difficult and error prone.
    The development of appropriate and well-validated analysis methods that do not produce statistical artifacts is still ongoing and is receiving much attention.
    Here, we perform a thorough analysis of each step in this process to determine the best tools and parameter choices that generate the most accurate and robust networks.
    Ultimately, we create a sequence analysis pipeline to standardize the processing of high-throughput community 16S rRNA sequencing data into networks of microbial interactions derived from their co-occurrences.
    \hl{The development of a standard pipeline for 16S data analysis would enable accurate comparison of data from different data-sets.} \todo[size=\footnotesize]{TODO: Talk briefly about the main result}
    The pipeline is available as a Python package and a docker container.
  }
\end{abstract}

% Insert keywords here
\keywords{Microbiome, 16S rRNA, Pipeline, Interaction, Network, Correlations, Qiime}
